---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hydrafit

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

The goal of hydrafit is to fit line parameters using a likelihood frame work for leaf hydraulic vulnerability curves. The functions included in the tests of the best fit are linear, logistic, sigmoidal, and two exponential functions. This package are provides support for the bootstrapping percent loss in hydraulic function as well as pairwise bootstrap comparisons. 

## Installation

You can install the development version of hydrafit from [GitHub](https://github.com/) with:

```{r eval=FALSE}
devtools::install_github("brownegm/hydrafit", build_vignettes = T)
```

## Example
An example of the use of the functions is available as a vignette. 
```{r eval=FALSE}
browseVignettes(package = "hydrafit")
```
The unrendered vignette is also available in vignettes folder as a .qmd file. 

