---
title: "How to fit hydraulics parameters"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to fit hydraulics parameters}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hydrafit)
library(here)
library(dplyr)

```

### Estimation of parameters

The aim of this vignette is to illustrate an example of estimating parameters and bootstrapping confidence intervals around the percent loss in hydraulic conductivity. The functions assume that the data is in organized by species, and includes at least leaf water potential value (often in MPa) and leaf hydraulic conductance or stomatal conductance measurements (often in mmols m^-2^ s\^-1). The data can be log adjusted if you'd like and put in the same data set using `data.type` column. The default is to add the column and input 1 for all entries.

```{r}
# load data


cebe <- cebe_efm %>%
  rename(species = Species, psi = Psi_lowest, kl = K) %>% # rename var names to fit with the rest of the syntax below.
  mutate(data.type = rep(1, dim(dd_full)[1])) %>%
  select(species.site, data.type, psi, kl) # function's expecting this order

#dd<-dd%>%select(!c(Individual,Leaf,site))

#data prep
dd$to_split = paste(dd$species.site, dd$data.type)
aggregate(dd, by =list(dd$to_split), FUN=length) -> speciesN
speciesN[which(speciesN$to_split > 5),1] -> species_list
#Trying to fit curves with less than 6 points returns -inf for the AICcor. Are those the binned data? Would it be possible to make the bins smaller so there are more points?

# first, just to make sure that things work as expected, let's print out
# the gs column for each species
for (ii in 1:length(species_list)){
  subset(dd, dd$to_split == species_list[ii], select =c(1:5)) -> data_by_sp
  print(data_by_sp)
}
# From Megan::I couldn't get the list format to save as a usable .csv file, so I changed everything to dataframes

# Line Fitting ------------------------------------------------------------

# Declare the data frame to store the results
modelfitting_results_linear <-
  data.frame(
    Species = as.character(),
    data.type = as.character(),
    A = numeric(),
    B = numeric(),
    C = numeric(),
    D = numeric(),
    loglikeli = numeric(),
    rsq = numeric(),
    slope = numeric(),
    AIC = numeric(),
    AICcorr = numeric(),
    sterror1 = numeric(),
    sterror2 = numeric(),
    sterror3 = numeric(),
    sterror4 = numeric(),
    N = numeric()
  )
modelfitting_results_logistic <-
  data.frame(
    Species = as.character(),
    data.type = as.character(),
    A = numeric(),
    B = numeric(),
    C = numeric(),
    D = numeric(),
    loglikeli = numeric(),
    rsq = numeric(),
    slope = numeric(),
    AIC = numeric(),
    AICcorr = numeric(),
    sterror1 = numeric(),
    sterror2 = numeric(),
    sterror3 = numeric(),
    sterror4 = numeric(),
    N = numeric()
  )
modelfitting_results_sigmoidal <-
  data.frame(
    Species = as.character(),
    data.type = as.character(),
    A = numeric(),
    B = numeric(),
    C = numeric(),
    D = numeric(),
    loglikeli = numeric(),
    rsq = numeric(),
    slope = numeric(),
    AIC = numeric(),
    AICcorr = numeric(),
    sterror1 = numeric(),
    sterror2 = numeric(),
    sterror3 = numeric(),
    sterror4 = numeric(),
    N = numeric()
  )
modelfitting_results_exp1 <-
  data.frame(
    Species = as.character(),
    data.type = as.character(),
    A = numeric(),
    B = numeric(),
    C = numeric(),
    D = numeric(),
    loglikeli = numeric(),
    rsq = numeric(),
    slope = numeric(),
    AIC = numeric(),
    AICcorr = numeric(),
    sterror1 = numeric(),
    sterror2 = numeric(),
    sterror3 = numeric(),
    sterror4 = numeric(),
    N = numeric()
  )
modelfitting_results_exp2 <-
  data.frame(
    Species = as.character(),
    data.type = as.character(),
    A = numeric(),
    B = numeric(),
    C = numeric(),
    D = numeric(),
    loglikeli = numeric(),
    rsq = numeric(),
    slope = numeric(),
    AIC = numeric(),
    AICcorr = numeric(),
    sterror1 = numeric(),
    sterror2 = numeric(),
    sterror3 = numeric(),
    sterror4 = numeric(),
    N = numeric()
  )

# use these gs's as inputs to the likelihood function
#Linear
pdf(file = here('outputs','Linear_fits.pdf'), width =8.5, height=5, onefile=T)
#Open a pdf file to save fitted curve plots in 
# #For every species, fit the curve and record the results  
cli::cli_progress_bar("Fitting curves (Linear)", total=length(species_list))
for (ii in 1:length(species_list)){
  (subset(dd, dd$to_split == species_list[ii], select =c(1:5)) -> data_by_sp)
  Linear_fits = fit_linear(data_by_sp, Linear, plot=F, xlab="Water Potential (-MPa)", ylab="Leaf Hydraulic Conductance (units)")
  Linear_fits$D.NA<- NA # placeholder to keep all of the data frames the same size
  Linear_fits$sterror.NA <- NA
  rbind(modelfitting_results_linear, as.data.frame(Linear_fits))-> modelfitting_results_linear
  #print(ii)
  cli::cli_progress_update()
} 

dev.off()

#estimate the pX values 
modelfitting_results_linear$psi_k20<- (0.8-1)*(-modelfitting_results_linear$A.A)*-1/(modelfitting_results_linear$B.B)
modelfitting_results_linear$psi_k50<- (0.5-1)*(-modelfitting_results_linear$A.A)*-1/(modelfitting_results_linear$B.B)
modelfitting_results_linear$psi_k80<- (0.2-1)*(-modelfitting_results_linear$A.A)*-1/(modelfitting_results_linear$B.B)
modelfitting_results_linear$psi_k95<- (0.05-1)*(-modelfitting_results_linear$A.A)*-1/(modelfitting_results_linear$B.B)


# PX values with max at 0.1 MPa
modelfitting_results_linear$gmax_at0.1 <- (modelfitting_results_linear$B.B*0.1)+modelfitting_results_linear$A.A
modelfitting_results_linear$psi_k20_at0.1<- ((0.8*modelfitting_results_linear$gmax_at0.1)-modelfitting_results_linear$A.A)/(modelfitting_results_linear$B.B)
modelfitting_results_linear$psi_k50_at0.1<- ((0.5*modelfitting_results_linear$gmax_at0.1)-modelfitting_results_linear$A.A)/(modelfitting_results_linear$B.B)
modelfitting_results_linear$psi_k80_at0.1<- ((0.2*modelfitting_results_linear$gmax_at0.1)-modelfitting_results_linear$A.A)/(modelfitting_results_linear$B.B)
modelfitting_results_linear$psi_k95_at0.1<- ((0.05*modelfitting_results_linear$gmax_at0.1)-modelfitting_results_linear$A.A)/(modelfitting_results_linear$B.B)

# #Every model has different formulas for k50 and k95
# which(is.na(as.numeric(modelfitting_results[,12]))=='TRUE' | is.na(as.numeric(modelfitting_results[,13]))=='TRUE'| is.na(as.numeric(modelfitting_results[,14]))=='TRUE') -> problem_rows
# 
# #Look for curves that returns NAs for the parameter error values
# write.csv(modelfitting_results, file = here('outputs',"Linear_fits.csv"))
# cat("Linear has ", length(problem_rows), "curve(s) with NAs: ", problem_rows)
# 

#Logistic
#Declare the pdf file to hold the plots
pdf(file = here('outputs','Logistic_fits.pdf'), width =8.5, height=5, onefile=T)
#Empty the data frame of the previous results
#modelfitting_results[FALSE,] -> modelfitting_results
cli::cli_progress_bar("Fitting curves (logistic)", total=length(species_list))
for (ii in 1:length(species_list)){
  subset(dd, dd$to_split == species_list[ii], select = c(1:5)) -> data_by_sp
  define_parsL(data_by_sp) -> par_estimates
  parsL=par_estimates[[1]]
  par_loL=par_estimates[[2]]
  par_highL=par_estimates[[3]]
  Logistic_fits = fit_nonlinear(data_by_sp, parsL, par_loL, par_highL, model_type = "log", plot=F)
  rbind(modelfitting_results_logistic, as.data.frame(Logistic_fits))-> modelfitting_results_logistic
  cli::cli_progress_update()
}

dev.off()

modelfitting_results_logistic$psi_k20<- modelfitting_results_logistic$C.Xo*(1/0.8-1)^(1/modelfitting_results_logistic$B.B)
modelfitting_results_logistic$psi_k50<- modelfitting_results_logistic$C.Xo*(1/0.5-1)^(1/modelfitting_results_logistic$B.B)
modelfitting_results_logistic$psi_k80<- modelfitting_results_logistic$C.Xo*(1/0.2-1)^(1/modelfitting_results_logistic$B.B)
modelfitting_results_logistic$psi_k95<- modelfitting_results_logistic$C.Xo*(1/0.05-1)^(1/modelfitting_results_logistic$B.B)

# PX values with max at 0.1 MPa
modelfitting_results_logistic$gmax_at0.1 <- (modelfitting_results_logistic$A.A)/(1+((0.1/modelfitting_results_logistic$C.Xo)^modelfitting_results_logistic$B.B))
modelfitting_results_logistic$psi_k20_at0.1<- (modelfitting_results_logistic$C.Xo)*(((modelfitting_results_logistic$A.A)/(0.8*modelfitting_results_logistic$gmax_at0.1)-1)^(1/modelfitting_results_logistic$B.B))
modelfitting_results_logistic$psi_k50_at0.1<- (modelfitting_results_logistic$C.Xo)*(((modelfitting_results_logistic$A.A)/(0.5*modelfitting_results_logistic$gmax_at0.1)-1)^(1/modelfitting_results_logistic$B.B))
modelfitting_results_logistic$psi_k80_at0.1<- (modelfitting_results_logistic$C.Xo)*(((modelfitting_results_logistic$A.A)/(0.2*modelfitting_results_logistic$gmax_at0.1)-1)^(1/modelfitting_results_logistic$B.B))
modelfitting_results_logistic$psi_k95_at0.1<- (modelfitting_results_logistic$C.Xo)*(((modelfitting_results_logistic$A.A)/(0.05*modelfitting_results_logistic$gmax_at0.1)-1)^(1/modelfitting_results_logistic$B.B))

# which(is.na(as.numeric(modelfitting_results[,12]))=='TRUE' | is.na(as.numeric(modelfitting_results[,13]))=='TRUE'| is.na(as.numeric(modelfitting_results[,14]))=='TRUE'| is.na(as.numeric(modelfitting_results[,15]))=='TRUE') -> problem_rows
# write.csv(modelfitting_results, file = here('outputs',"Logistic_fits.csv"))
# cat("Logistic has ", length(problem_rows), "curve(s) with NAs: ", problem_rows)


#Sigmoidal
#Declare the pdf file to hold the plots
pdf(file = here('outputs','Sigmoidal_fits.pdf'), width =8.5, height=5, onefile=T)
##Empty the data frame of results
#modelfitting_results[FALSE,] -> modelfitting_results
cli::cli_progress_bar("Fitting curves (Sigmoidal)", total=length(species_list))
for (ii in 1:length(species_list)){
  subset(dd, dd$to_split == species_list[ii], select =c(1:5)) -> data_by_sp
  define_parsS(data_by_sp) -> par_estimates
  parsS=par_estimates[[1]]
  par_loS=par_estimates[[2]]
  par_highS=par_estimates[[3]]
  Sigmoidal_fits = fit_nonlinear(data_by_sp, parsS, par_loS, par_highS, model_type= "sig", plot=F)
  rbind(modelfitting_results_sigmoidal, as.data.frame(Sigmoidal_fits))-> modelfitting_results_sigmoidal
  cli::cli_progress_update()
}
#dev.off()

modelfitting_results_sigmoidal$psi_k20<- modelfitting_results_sigmoidal$C.Xo - modelfitting_results_sigmoidal$B.B*log(1/0.8 -1)
modelfitting_results_sigmoidal$psi_k50<- modelfitting_results_sigmoidal$C.Xo - modelfitting_results_sigmoidal$B.B*log(1/0.5 -1)
modelfitting_results_sigmoidal$psi_k80<- modelfitting_results_sigmoidal$C.Xo - modelfitting_results_sigmoidal$B.B*log(1/0.2 -1)
modelfitting_results_sigmoidal$psi_k95<- modelfitting_results_sigmoidal$C.Xo - modelfitting_results_sigmoidal$B.B*log(1/0.05 -1)

# PX values with max at 0.1 MPa
modelfitting_results_sigmoidal$gmax_at0.1 <- (modelfitting_results_sigmoidal$A.A)/(1+exp(-((0.1-modelfitting_results_sigmoidal$C.Xo)/modelfitting_results_sigmoidal$B.B)))
modelfitting_results_sigmoidal$psi_k20_at0.1<- -modelfitting_results_sigmoidal$B.B*(modelfitting_results_sigmoidal$A.A-(0.8*modelfitting_results_sigmoidal$gmax_at0.1)-log(0.8*modelfitting_results_sigmoidal$gmax_at0.1)) + modelfitting_results_sigmoidal$C.Xo
modelfitting_results_sigmoidal$psi_k50_at0.1<- -modelfitting_results_sigmoidal$B.B*(modelfitting_results_sigmoidal$A.A-(0.5*modelfitting_results_sigmoidal$gmax_at0.1)-log(0.5*modelfitting_results_sigmoidal$gmax_at0.1)) + modelfitting_results_sigmoidal$C.Xo
modelfitting_results_sigmoidal$psi_k80_at0.1<- -modelfitting_results_sigmoidal$B.B*(modelfitting_results_sigmoidal$A.A-(0.2*modelfitting_results_sigmoidal$gmax_at0.1)-log(0.2*modelfitting_results_sigmoidal$gmax_at0.1)) + modelfitting_results_sigmoidal$C.Xo
modelfitting_results_sigmoidal$psi_k95_at0.1<- -modelfitting_results_sigmoidal$B.B*(modelfitting_results_sigmoidal$A.A-(0.05*modelfitting_results_sigmoidal$gmax_at0.1)-log(0.05*modelfitting_results_sigmoidal$gmax_at0.1)) + modelfitting_results_sigmoidal$C.Xo


# which(is.na(as.numeric(modelfitting_results[,12]))=='TRUE' | is.na(as.numeric(modelfitting_results[,13]))=='TRUE'| is.na(as.numeric(modelfitting_results[,14]))=='TRUE'| is.na(as.numeric(modelfitting_results[,15]))=='TRUE') -> problem_rows
# write.csv(modelfitting_results, file = here('outputs',"Sigmoidal_fits.csv"))
# cat("Sigmoidal has ", length(problem_rows), "curve(s) with NAs: ", problem_rows)

#Exponential
pdf(file = here('outputs','Exponential_fits.pdf'), width =8.5, height=5, onefile=T)
#modelfitting_results[FALSE,] -> modelfitting_results
cli::cli_progress_bar("Fitting curves (Exponential)", total=length(species_list))
for (ii in 1:length(species_list)){
  subset(dd, dd$to_split == species_list[ii], select =c(1:5)) -> data_by_sp
  define_parsE(data_by_sp) -> par_estimates
  parsE=par_estimates[[1]]
  par_loE=par_estimates[[2]]
  par_highE=par_estimates[[3]]
  Exponential_fits = fit_nonlinear(data_by_sp, parsE, par_loE, par_highE, model_type = "exp", plot=F)
  Exponential_fits$D.NA<- NA 
  Exponential_fits$sterror.NA <- NA
  rbind(modelfitting_results_exp1, as.data.frame(Exponential_fits))-> modelfitting_results_exp1
  cli::cli_progress_update()
}
dev.off()

modelfitting_results_exp1$psi_k20<- log(0.8)/(-modelfitting_results_exp1$B.B)
modelfitting_results_exp1$psi_k50<- log(0.5)/(-modelfitting_results_exp1$B.B)
modelfitting_results_exp1$psi_k80<- log(0.2)/(-modelfitting_results_exp1$B.B)
modelfitting_results_exp1$psi_k95<- log(0.05)/(-modelfitting_results_exp1$B.B)

# PX values with max at 0.1 MPa
modelfitting_results_exp1$gmax_at0.1 <- modelfitting_results_exp1$A.A * exp(-modelfitting_results_exp1$B.B*0.1)
modelfitting_results_exp1$psi_k20_at0.1<- (log((0.8*modelfitting_results_exp1$gmax_at0.1)/modelfitting_results_exp1$A.A))/(-modelfitting_results_exp1$B.B)
modelfitting_results_exp1$psi_k50_at0.1<- (log((0.5*modelfitting_results_exp1$gmax_at0.1)/modelfitting_results_exp1$A.A))/(-modelfitting_results_exp1$B.B)
modelfitting_results_exp1$psi_k80_at0.1<- (log((0.2*modelfitting_results_exp1$gmax_at0.1)/modelfitting_results_exp1$A.A))/(-modelfitting_results_exp1$B.B)
modelfitting_results_exp1$psi_k95_at0.1<- (log((0.05*modelfitting_results_exp1$gmax_at0.1)/modelfitting_results_exp1$A.A))/(-modelfitting_results_exp1$B.B)

# which(is.na(as.numeric(modelfitting_results[,12]))=='TRUE' | is.na(as.numeric(modelfitting_results[,13]))=='TRUE'| is.na(as.numeric(modelfitting_results[,14]))=='TRUE') -> problem_rows
# write.csv(modelfitting_results, file = here('outputs',"Exponential_fits.csv"))
# cat("Exponential has ", length(problem_rows), "curve(s) with NAs: ", problem_rows)

#Exponential2
pdf(file = here('outputs','Exponential2_fits.pdf'), width =8.5, height=5, onefile=T)
#modelfitting_results[FALSE,] -> modelfitting_results
cli::cli_progress_bar("Fitting curves (Exponential 2)", total=length(species_list))
for (ii in 1:length(species_list)){
  subset(dd, dd$to_split == species_list[ii], select =c(1:5)) -> data_by_sp
  define_parsE2(data_by_sp) -> par_estimates
  parsE2=par_estimates[[1]]
  par_loE2=par_estimates[[2]]
  par_highE2=par_estimates[[3]]
  Exponential2_fits = fit_nonlinear(data_by_sp,  parsE2, par_loE2, par_highE2, model_type= "exp2", plot=F)
  #########Update from Megan: this fit returns NaN (not a number) or "N/A" instead of NA at times (probably when C is very small),
  ####and this converts everything else in the modelfitting_results columns to NA-
  ###this replaces the NaNs with -999, so they'll be easy to find
  Exponential2_fits[which(is.na(Exponential2_fits)== TRUE)] = -999
  Exponential2_fits[which(Exponential2_fits== "N/A")] = -999

  rbind(modelfitting_results_exp2, as.data.frame(Exponential2_fits))-> modelfitting_results_exp2
  cli::cli_progress_update()
}

dev.off()

modelfitting_results_exp2$psi_k20<- log(0.8- modelfitting_results_exp2$C.C/modelfitting_results_exp2$A.A)/(-modelfitting_results_exp2$B.B)
modelfitting_results_exp2$psi_k50<- log(0.5- modelfitting_results_exp2$C.C/modelfitting_results_exp2$A.A)/(-modelfitting_results_exp2$B.B)
modelfitting_results_exp2$psi_k80<- log(0.2- modelfitting_results_exp2$C.C/modelfitting_results_exp2$A.A)/(-modelfitting_results_exp2$B.B)
modelfitting_results_exp2$psi_k95<- log(0.05- modelfitting_results_exp2$C.C/modelfitting_results_exp2$A.A)/(-modelfitting_results_exp2$B.B)

# PX values with max at 0.1 MPa
modelfitting_results_exp2$gmax_at0.1 <- modelfitting_results_exp2$C.C+(modelfitting_results_exp2$A.A * exp(-modelfitting_results_exp2$B.B*0.1))
modelfitting_results_exp2$psi_k20_at0.1<- -((log(((0.8*modelfitting_results_exp2$gmax_at0.1)-modelfitting_results_exp2$C.C)/modelfitting_results_exp2$A.A))/(modelfitting_results_exp2$B.B))
modelfitting_results_exp2$psi_k50_at0.1<- -((log(((0.5*modelfitting_results_exp2$gmax_at0.1)-modelfitting_results_exp2$C.C)/modelfitting_results_exp2$A.A))/(modelfitting_results_exp2$B.B))
modelfitting_results_exp2$psi_k80_at0.1<- -((log(((0.2*modelfitting_results_exp2$gmax_at0.1)-modelfitting_results_exp2$C.C)/modelfitting_results_exp2$A.A))/(modelfitting_results_exp2$B.B))
modelfitting_results_exp2$psi_k95_at0.1<- -((log(((0.05*modelfitting_results_exp2$gmax_at0.1)-modelfitting_results_exp2$C.C)/modelfitting_results_exp2$A.A))/(modelfitting_results_exp2$B.B))


#########Update from Megan: these are the functions for psi at different k thresholds
# which(is.na(as.numeric(modelfitting_results[,12]))=='TRUE' | as.numeric(modelfitting_results[,12])==-999 |is.na(as.numeric(modelfitting_results[,13]))=='TRUE'| as.numeric(modelfitting_results[,13])==-999 | is.na(as.numeric(modelfitting_results[,14]))=='TRUE'| as.numeric(modelfitting_results[,14])==-999 ) -> problem_rows
# write.csv(modelfitting_results, file = here('outputs',"Exponential2_fits.csv"))
# cat("Exponential2 has ", length(problem_rows), "curve(s) with NAs: ", problem_rows)


#excel file with all the fits for each species.

# Bootstrapping Psi_KXX ---------------------------------------------------

#source bootstrap function
#source(here("r_script", "boot.R"))

#standard error function
se<-function(x){
  sd(x, na.rm = T)/sqrt(length(x))# specifying na.rm=T because sometimes the predicted parameters estimate negative values and log(negative #)=NA
}

#rename files for concision and legibility
df_lin<-modelfitting_results_linear
df_sig<-modelfitting_results_sigmoidal
df_log<-modelfitting_results_logistic
df_exp1<-modelfitting_results_exp1
df_exp2<-modelfitting_results_exp2

mod_bestfit_temp<-fx_select(df_lin, df_log, df_sig, df_exp1, df_exp2)#produce df with the best model fit for each species

# some of the fits do not match the data well. Here I remove the ones that don't and replace them with 
# others as long as the replacement is less than or equal to 2 AICcorr values. Luckily, the better option for all is logistic
mod_bestfit_temp<-mod_bestfit_temp%>%
  filter(!species%in%c("HF_QURU", 'MOF_QUAL', "SCBI_QUAL", 'SCBI_QURU', 'SCBI_QUVE', "SJER_QUWI", "OSBS_PIPA"))%>%
  mutate_at(3:26, as.numeric)
  
df_log_newbest<-df_log%>%
  filter(Species%in%c("HF_QURU", 'MOF_QUAL', "SCBI_QUAL", 'SCBI_QURU', 'SCBI_QUVE', "SJER_QUWI", "OSBS_PIPA"))%>%
  mutate_at(3:26, as.numeric)

names(df_log_newbest)<-names(mod_bestfit_temp)# names don't match before this; now they do

#put it all together now
mod_bestfit<-rbind(mod_bestfit_temp, df_log_newbest)

##
# boot_v2<-booty(version=2)
# mod_bestfit<-mod_bestfit_temp

#output_v1<-data.frame(species=character(), pred_mean=numeric(), pred_median=numeric(), pred_se=numeric(), conf_low=numeric(), conf_high=numeric())
output_boot <-
  data.frame(
    species = character(),
    pred_mean = numeric(),
    pred_median = numeric(),
    pred_se = numeric(),
    conf_low = numeric(),
    conf_high = numeric()
  )

alpha=0.05

set.seed(1994)

for( i in 1:dim(mod_bestfit)[1]){
  print(i)
  suppressWarnings(boot_vals<-bootPX(mod_bestfit,
                    fx_type=mod_bestfit[i,"data.type"], 
                    px=0.5)%>%unlist())# suppressing warnings for the NAs that are produced
  
  boot_mean<-mean(boot_vals, na.rm=T)# specifying na.rm=T because sometimes the predicted parameters estimate negative values and log(negative #)=NA
  
  boot_se<-se(boot_vals)
  
  boot_median<-median(boot_vals,na.rm = T)# specifying na.rm=T because sometimes the predicted parameters estimate negative values and log(negative #)=NA
  #determine confidence intervals
  deg_of_freedom= length(boot_vals)
  t_score=qt(p=alpha/2, df=deg_of_freedom, lower.tail = F)
  
  margin_error<-t_score*boot_se
  
  conf.low<-mod_bestfit[i,"psi_k50"]-margin_error # using the predicted pX value to make the error make sense
  conf.high<-mod_bestfit[i,"psi_k50"]+margin_error
  
  output_boot[i,1]<-mod_bestfit[i,"species"]
  output_boot[i,2]<-boot_mean
  output_boot[i,3]<-boot_median
  output_boot[i,4]<-boot_se
  output_boot[i,5]<-conf.low
  output_boot[i,6]<-conf.high
}

```
